Twisted eleven-dimensional supergravity

### 2021-11-04 nonmin.tex
eager/hahner

We will show that the non-minimal twist is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument. This confirms a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}).

>>>>

We will show that the non-minimal twist is equivalent to an interacting theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument. This completes the confirmation of a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}); the result was checked at the level of the free theory in~\cite{EagerHahner} by computing the nonminimal twist of the eleven-dimensional multiplet directly at the component-field level.
